---
output: github_document
title: "Small Project Examining Einstein Citations"
author: "David Gerard"
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

This small project just creates some plots of Einstein's citation counts, as measured by [Scopus](https://www.scopus.com/home.uri).

The files after everything is evaluated are:

```{r}
list.files(recursive = TRUE)
```


These files have the following dependency structure:

```{r dependency-graph, message = FALSE, echo = FALSE, fig.width=10}
library(tidyverse)
library(ggdag)
set.seed(15)
dagify("ein_long.csv" ~ "ein_tidy.R",
       "ein_long.csv" ~ "ein_cites.csv",
       "ein_tot.csv" ~ "ein_calc_tot.R",
       "ein_tot.csv" ~ "ein_long.csv",
       "citefig.png" ~ "all_paper_fig.R",
       "citefig.png" ~ "ein_long.csv",
       "paper_hist.png" ~ "make_hist.R",
       "paper_hist.png" ~ "ein_tot.csv",
       "ein_report.html" ~ "ein_report.Rmd",
       "ein_report.html" ~ "citefig.png",
       "ein_report.html" ~ "paper_hist.png",
       "ein_report.html" ~ "ein_tot.csv") %>%
  ggdag(layout = "sugiyama",
        text_col = "black",
        node = FALSE) +
  theme_void() +
  xlim(-0.5, 5.5)
```

Modify the Makefile to automatically evaluate this pipeline. You can always check if the Makefile works by deleting everything in the output folder and rerunning `make` in the terminal. If "analysis/ein_report.html" is re-generated, then you are good to go.
